\cvsection{Education}
\cvevent{B.E. in Computer Science  - 8.08  CGPA}{ANNA UNIVERSITY}{ MARCH 2019}{}
\cvevent{Higher Secondary - 96.25\%}{SRI VENKATESWARA VIDHYA MANTHIR}{ MARCH 2015}{}
\cvevent{Secondary - 10CGPA }{SKNS PMC VIVEKANANDA VIDYALAYA}{MARCH 2013}{}
\cvsection{Projects}
\cvproject{Automatic Answer Sheets Evaluator}
\begin{itemize}
\item An android and web-integrated application built on Python and interfaced with Django framework to make the answer paper evaluation go digital.
\end{itemize}
\smallskip
\smallskip
\cvproject{BuzzBook}
\begin{itemize}
\item A Pega based application to post movie shows for the theatre owners and book movie tickets for the end customers online. It uses REST integration simulated for payments through credit/debit cards.
\end{itemize}
\smallskip
\smallskip
\cvproject{Bestow}
\begin{itemize}
\item A progressive web and android integrated application as a platform for people to donate books, food, blood, etc. built on Bootstrap framework using HTML, CSS and Jscript with Android Studio.
\end{itemize}
\smallskip
\smallskip
\cvproject{Electronic Voting Machine}
\begin{itemize}
\item Developed an embedded system using ULK (Universal Learning Kit) to build an electronic voting machine in C and UNIX.
\end{itemize}
\smallskip
\smallskip
\cvproject{Callum}
\begin{itemize}
\item Developed a progressive speech emotion recognition model using python librosa and sklearn.
\end{itemize}
\smallskip
\smallskip
\cvproject{Virtual Keylogger}
\begin{itemize}
\item Developed a keystroke logger model to capture both keys struck on the keyboard as well as a virtual keyboard.
\end{itemize}
\cvsection{Publications}
\smallskip
\begin{itemize}
\item Knowledge Representation and Answer Evaluation System using Language Processing Algorithm.
\item Detection of Endangered Gangetic Dolphins from Underwater Videos Using Improved Hybrid Frame Detection.
\clearpage
\end{document}
